\hypertarget{index_intro_sec}{}\section{Introduction}\label{index_intro_sec}
This is the documentation of the Atari Jaguar C library. This library is intended to implement eventually a full ANSI C library. It has been especially targeted for the Atari Jaguar since some parts are written in assembler and takes into account some specifities of this platform. In addition, this C library contains the source of a generic startup code for the Atari Jaguar (crt0.s).\hypertarget{index_Installation}{}\section{Installation}\label{index_Installation}
The easiest way to install this library is to get your hands on a binary distribution of it. Then copy the header files in a directory where your C compiler will look after (include directory) and the objects and archive files in a directory where your linker will look after (lib directory).

Provided that your compilation environment is correctly set up, you can also alternatively build the library with the 'make' command and then install it where you want with the 'make install' command. You might have to change the TARGET variable of the Makefile to indicate where you want all the files to be copied.\hypertarget{index_license_sec}{}\section{License}\label{index_license_sec}
The following license applies to every file of the distribution but except the file jaguar.inc.

Copyright (C) 2006 Seb/The Removers \href{http://removers.atari.org/}{\tt http://removers.atari.org/}

This library is free software; you can redistribute it and/or modify it under the terms of the GNU Lesser General Public License as published by the Free Software Foundation; either version 2.1 of the License, or (at your option) any later version.

This library is distributed in the hope that it will be useful, but WITHOUT ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the GNU Lesser General Public License for more details.

You should have received a copy of the GNU Lesser General Public License along with this library; if not, write to the Free Software Foundation, Inc., 51 Franklin Street, Fifth Floor, Boston, MA 02110-1301 USA 